Title

### 2019-05-20 10_applications.tex
description of 2D lithophanes

\section{Applications}
\subsection{3D Lithophane}
``The illuminance $E_\text{p}$ lux at a location $d$ metres from a point source of intensity $I$ candela is given by the cosine law of illumination,
$E_\text{p} = I \cos \theta / d^2$.''\cite{snow2001plant}
We relate the distances to the model: $E_\text{p} = I \cos \theta / (d_\text{rel} \cdot d_\text{max})^2 = d_\text{max}^2 I \cos \theta / d_\text{rel}^2$.
The scaling factor $d_\text{max}^2 I$ depends on the light source (intensity and location) and the 3D model.

>>>>

\section{Applications}

\subsection{2D Lithophane}
A user sets the minimum thickness  $n$ and maximum thickness $m$.
Based on the material parameter transmittance $t$ as percentage of light after 1mm (more) thickness,
we calculate the thickness $h$ at each location based on the luminance $I$ there:
\begin{align}
p &= \frac{1}{\log_2 t}
\\
b &= 2^{(m-n)/p}
\\
h &= n + p \log_2 ( b + (1-b) I )
\end{align}

\begin{figure}[H]
\centering
\includegraphics[width=.75\columnwidth]{sources/litho/luminance_to_thickness.pdf}
\caption{Mapping luminance to height for 2D lithophanes.}
\label{luminance_to_thickness}
\end{figure}

\subsection{3D Lithophane}
``The illuminance $E_\text{p}$ lux at a location $d$ metres from a point source of intensity $I$ candela is given by the cosine law of illumination,
$E_\text{p} = I \cos \theta / d^2$.''\cite{snow2001plant}
We relate the distances to the model: $E_\text{p} = I \cos \theta / (d_\text{rel} \cdot d_\text{max})^2 = d_\text{max}^2 I \cos \theta / d_\text{rel}^2$.
The scaling factor $d_\text{max}^2 I$ depends on the light source (intensity and location) and the 3D model.
